Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-07-25 R0V0.tex
> Done: Started to remove all files that are not the TeX file. Add information about graphs.

@@

{\itshape Stabilizability Notion.} A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$, denoted as $k^\ast(\cdot,\cdot,X^\ast,u^\ast)$, such that the inequality
\begin{equation}\label{eq:global exponential uniform stabilizability}
	\left|X(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
\end{equation}
holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}). Note that this not is a particular case of \emph{incremental asymptotic stability}, the interested reader may address \cite{Forni2014,Forni2014a} for further information on this stability concept.

@@

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}.
\end{definition}

@@

The authors plan to extend this work for the synthesis of event-based controllers, and the analysis of disturbances such as time delays.

{\itshape Acknowledgments.} The authors thank the anonymous reviewers.

>>>>

Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise.

@@

{\itshape Stabilizability Notion.} A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$, denoted as $k^\ast(\cdot,\cdot,X^\ast,u^\ast)$, such that the inequality
\begin{equation}\label{eq:global exponential uniform stabilizability}
	\left|X(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
\end{equation}
holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}).

@@

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes it.
\end{definition}

@@
